Incentivizing Exploration with Unbiased History

### 2018-10-27 model.tex
commit early and often!

%!TEX root = main.tex
\section{Our Model}
\label{sec:model}

@@

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveals
a sequence of messages accroding to a disclosure policy so that the
regret of the induced sequence of actions is minimized. We will focus
on \emph{unbiased sub-history policies} that at each round $t$ reveal
the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such
that each $S_t\subseteq [t-1]$ is a subset of previous rounds
\emph{fixed ahead of time}. A simple example is the policy that
reveals the \emph{full history} with $S_t = [t-1]$.  All of the
policies we develop are \emph{transitive}: for any two agents $t$ and
$t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
that of $S_{t'}$.

@@

\xhdr{Agents' behavior.} We model agents with heterogeneity in their
arm selections. In particular, each agent $t$ has a private estimator
that maps the revealed sub-history $H_t$ to a mean reward estimate
$\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$
with the highest estimate. The agents' private estimators are drawn
i.i.d.~from an unknown distribution. For any $t\in[T]$ and $a\in \A$,
we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls
of $a$ and the empirical mean reward of arm $a$ in $H_t$
respectively. If an arm is not pulled in $H_t$, we will let
$\bar{\mu}_a^t = 0$.

@@

We will make the following assumptions on the set of mean rewards
$\{\mu_a\}$, and the relationship between the estimates $\hat \mu_a^t$
and empirical mean rewards $\bar\mu_a^t$.

\begin{assumption}
\label{ass:embehave}
Let $c_m = 1/16$.\swcomment{maybe use a better notation} 
% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
\begin{itemize}
\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
  of $[1/3, 2/3]$.

\item There exists a constant $c_T$ such that for any agent $t$ and
  arm $a$, as long as $t_a \geq c_T$,
\[
  \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
  \frac{c_m}{\sqrt{N_{t,a}}}.
\]
\item In the case of $N_{t,a} = 0$, the initial estimate
  $\hat{\mu}^t_a$ is at least $1/3$.
\end{itemize}
\end{assumption}

@@

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.
% \swcomment{why independently? can be be
%   adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial. It's fairly annoying for the anti-concentration argument. In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty}
\end{remark}

Given any bandit instance, we can also define the \emph{gap parameter}
$\Delta$ as the difference between the largest and second largest mean
rewards. In general, the gap parameter is unknown to the principal (or
the algorithm), but we also show how we can obtain different forms of
regret bounds if $\Delta$ is known.

>>>>

%!TEX root = main.tex
\section{Model}
\label{sec:model}

@@

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal
a sequence of messages accroding to a disclosure policy so that the
regret of the induced sequence of actions is minimized. We will focus
on \emph{unbiased sub-history policies} that at each round $t$ reveal
the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such
that each $S_t\subseteq [t-1]$ is a subset of previous rounds
\emph{fixed ahead of time}. A simple example is the policy that
reveals the \emph{full history} with $S_t = [t-1]$.  All of the
policies we develop are \emph{transitive}: for any two agents $t$ and
$t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
that of $S_{t'}$.

@@

\xhdr{Agents' behavior.} We model agents with heterogeneity in their arm selections. In particular, each agent $t$ has a private estimator that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$ with the highest estimate. The agents' private estimators are drawn i.i.d.~from an unknown distribution. For any $t\in[T]$ and $a\in \A$, we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of $a$ and the empirical mean reward of arm $a$ in sub-history $H_t$ respectively. If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.  We require the following assumptions.

@@

\begin{assumption}
\label{ass:embehave}
The set of mean rewards $\{\mu_a\}$, the estimates $\hat \mu_a^t$, and the empirical mean rewards $\bar\mu_a^t$  satisfy:

\begin{itemize}
\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
  of $[1/3, 2/3]$.

\item Let $c_m = 1/16$.\swcomment{maybe use a better notation} \nicomment{yeah, why the subscript $m$? and $T$ below? how about just $\alpha,\beta$ for the constants in this assumption? or $\alpha$ and $N_0$? or use $n_{t,a}$ for number of pulls and $N$ for a constant that you want the $n_{t,a}$ to exceed?}
% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
There exists a constant $c_T$ such that for any agent $t$ and
  arm $a$, as long as \niedit{$N_{t,a} \geq c_T$}, 
\[
  \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
  \frac{c_m}{\sqrt{N_{t,a}}}.
\]
\item If $N_{t,a} = 0$, the initial estimate
  $\hat{\mu}^t_a$ is at least $1/3$.
\end{itemize}
\end{assumption}

@@

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.
% \swcomment{why independently? can be be
%   adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial. It's fairly annoying for the anti-concentration argument. In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty} \nicomment{need to at least say if we rule out rational agents with these assumptions (which I don't think is a disaster).}
\end{remark}

Given any bandit instance, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards. In general, the gap parameter is unknown to the principal (or the algorithm), but we show how to obtain different forms of regret bounds if $\Delta$ is known.
